Dac Summary

### 2020-11-24 dac_summary.Rmd
Add files via upload
updates

>>>>

#make a column that indicates whether or not accession number in melissa's is in my group
melissa_xls$overlap <- ((melissa_xls$ACCESSION_NUM) %in% (data_empi_acc_f_phq$ACCESSION_NUM))

#grab unique accession numbers that are NOT in the overlap group 
unique_access_nums_only_melissas_group <- melissa_xls$ACCESSION_NUM[which(!melissa_xls$overlap)]
names(unique_access_nums_only_melissas_group) <- c("count", "accession_num")

#write table, n = 14785
write.table(file = "/Users/eballer/BBL/msdepression/data/dac/unique_access_nums_in_melissas_group_from_mri_file_upd_w_empi.csv", x = unique_access_nums_only_melissas_group, sep = ",", col.names = TRUE, row.names = FALSE)
